Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-30 prob.tex
prob.tex Saperate two sections: Theorems and Proofs...

\section{Proof}

@@

>>>>

\section{Theorems}

@@

\section{Proofs}

\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
and there is a point~$\ket{\psi}\in S^{2}$, then the oscillation
on any latitude of the symmetrization of $f$ with respect to $\ket{\psi}$
is?\qed\end{lemma}
\begin{proof}
Consider $\ket{\psi}$ to be the north pole of $S^{2}$. Let $g$
be the symmetrization of $f$ with respect to $\ket{\psi}$, and $\eta=f\left(\ket{\psi}\right)$.
Let 
\begin{eqnarray*}
\omega_{f}\left(\delta\right) & = & \sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|\\
\omega_{g}\left(\delta\right) & = & \sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|g\left(\ket{\psi}\right)-g\left(\ket{\phi}\right)\right|=2\omega_{f}\left(\delta\right)
\end{eqnarray*}
Then, for any latitude $\theta_{0}$, the oscillation of $g$ on the
polar cap of latitude $2\theta_{0}-\frac{\pi}{2}$ is less than $\omega_{g}\left(2\sin2\theta_{0}\right)=2\omega_{f}\left(2\sin2\theta_{0}\right)$.

Let $\ket{\phi}$ and $\ket{\phi'}$ be points in the northern hemisphere
with the same latitude~$\theta$. If $\theta>2\theta_{0}-\frac{\pi}{2}$,
both $\ket{\phi}$ and $\ket{\phi'}$ are in the polar cap, so $\left|g\left(\ket{\phi}\right)-g\left(\ket{\phi'}\right)\right|<\omega_{g}\left(2\sin2\theta_{0}\right)=2\omega_{f}\left(2\sin2\theta_{0}\right)$.
Otherwise, consider $\theta\le2\theta_{0}-\frac{\pi}{2}$. Let $a$
be the difference in longitudes of $\ket{\phi}$ and $\ket{\phi'}$.
Take $n$ steps along east-west great circles to go from $\ket{\phi'}$
to a point $\ket{\phi_{s}}$ due south of $\ket{\phi}$. The difference
in latitude between $\ket{\phi}$ and $\ket{\phi_{s}}$ is at most
$\frac{a^{2}}{n}$, while, from (Lemma 16 to be typed),
\[
g\left(\ket{\phi_{s}}\right)\ge g\left(\ket{\phi'}\right)-n\left[2f\left(\ket{\psi}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\phi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)
\]
When the difference in latitude between $\ket{\phi}$ and $\ket{\phi_{s}}$
is at most $\frac{a^{2}}{n}$, the length between $\ket{\phi}$ and
$\ket{\phi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
and hence 
\[
g\left(\ket{\phi}\right)\ge g\left(\ket{\phi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\phi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
\]
for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.
\end{proof}
